### 2020-12-02 ch02_scientific_background/scientific_background.tex
Started section on antrhopogenic influence on carbon cycle

>>>>

\subsection{Anthropogenic Perturbations}
\label{subsec:02:carbon_cycle_perturbations}

Before the Industrial Era, the global carbon cycle was roughly in equilibrium.
This can be inferred from ice core measurements, which show an almost constant
atmospheric \ac{CO2} concentration over the last several thousand years before
the Industrial Revolution in the \nth{19} century \autocite{Ciais2013}. Since
the beginning of the Industrial Era, humanity is constantly emitting
carbon-based \acp{GHG} (\eg{} \ac{CO2} and \ac{CH4}) into the atmosphere.
Especially the atmospheric \ac{CO2} concentration has substantially increased,
which has already been shown by Charles D. Keeling in 1976 by his continuous
\ac{CO2} measurements at Mauna Loa, Hawaii that started in 1958
\autocite{Keeling1976}. From 1958, the atmospheric \ac{CO2} concentration at
Mauna Loa has steadily increased by about $100 \unit{ppm}$ to $410 \unit{ppm}$
in the year 2019 \autocite{Keeling2005}. In addition to the monotonic increase,
the so-called \enquote{Keeling Curve} is further superimposed with the seasonal
\ac{CO2} cycle, which gives rise to local maxima of the atmospheric \ac{CO2}
concentration in the Northern hemisphere winter and local minima in the
Northern hemisphere summer \autocite[see
\cref{subsec:02:carbon_cycle_overview}]{Keeling1995}. Due to its location in
the middle of the Pacific Ocean, the Mauna Loa Observatory offers perfect
conditions for \ac{CO2} measurements by being far away from big population
centers. Moreover, its elevation of more than $3000 \unit{m}$ provides access
to the well-mixed air of the Pacific Ocean in high altitudes, which prevents
any interference from the vegetation present on the Hawaiian Islands.

Apart from warming the Earth by altering its radiation budget, the emitted
\ac{CO2} directly influences the carbon exchange fluxes of the global carbon
cycle. which introduced net carbon fluxes between the different carbon
reservoirs into the system, which left this steady state in shows ...
